Quantum Interval-Valued Probability: Measurement and Probability

### 2017-11-08 prop_iop.tex
prop_iop.tex \subsection{Convexity and Core} Updating...

is true when when $P_{0}=\mathbb{1}$.

@@

are not commuting. Hence,
\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\unknown+\imposs=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.

@@

holds when $P_{0}=\proj{\psi}\in\mathcal{S}$. By lemma~\ref{lemma:quantum-convex-condition-lemma},
equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}) is
also true when when $P_{0}=\mathbb{1}-\proj{\psi}$, where $\proj{\psi}\in\mathcal{S}$.
\item If neither the above two cases holds, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\unknown+\unknown=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.

@@

for any~$P$, the state~$\rho$ must satisfy $\mu_{\rho}^{\mathrm{B}}(P)$

>>>>

when $P_{0}=\mathbb{1}$.

@@

are not commuting. Hence,$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\unknown+\imposs=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.

@@

holds when $P_{0}=\proj{\psi}\in\mathcal{S}$.
\item When $P_{0}=\mathbb{1}-\proj{\psi}$ for $\proj{\psi}\in\mathcal{S}$,
equation~(\ref{eq:QuantumInterval-valuedProbability-Convex}) follows
from the previous case with lemma~\ref{lemma:quantum-convex-condition-lemma}.
\item If neither the above cases holds, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\unknown+\unknown=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.

@@

for any~$P$, the state~$\rho$ must satisfy $\mu_{\rho}^{\mathrm{B}}(P)=0$
